---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

# CHL5222 Final Project
# Breastfeeding and HIV exposure on infant growth
# Main outcome: weight-for-length z-score (zwfl)
# Secondary outcome: head circumference z-score (zhc)

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(splines)
library(emmeans)
library(ggeffects)
library(broom.mixed)
library(patchwork)
library(janitor)
library(naniar)

```

## Import data 
```{r}
dat <- read.csv("hiv.csv", stringsAsFactors = FALSE) |>
  clean_names()
```

## Variable Descriptions

The dataset contains repeated growth measurements of infants followed from birth to 24 months to evaluate the relationship between HIV exposure, breastfeeding, and infant growth.

- `newid`  
  Unique identifier for each infant. Used to link repeated observations from the same child in longitudinal analysis.

- `visit`  
  Study visit number when the measurement was collected.

- `infage_month`  
  Infant age in months at the time of measurement. This variable represents the time dimension in the longitudinal analysis.

- `zwfl`  
  Weight-for-length z-score. This standardized measure compares an infant’s weight relative to their length based on WHO growth standards and is used as the primary growth outcome.

- `zhc`  
  Head circumference z-score. This standardized measure reflects head growth relative to age and is considered a secondary growth outcome.

- `enrol_hiv_status_cat`  
  Maternal HIV status at enrollment. This variable defines whether the infant was exposed to HIV during pregnancy (CHEU) or not exposed (CHU).

- `ebf_updated`  
  Exclusive breastfeeding status. Indicates whether the infant was exclusively breastfed.

- `bf_current_1year`  
  Current breastfeeding status. Indicates whether the infant is currently being breastfed at the time of observation.

- `b1_sex`  
  Infant sex.

- `gestage_final`  
  Gestational age at birth (in weeks). This variable accounts for differences in growth related to prematurity.

- `momage_cat`  
  Maternal age category at the time of delivery.

- `educ_cat_n`  
  Maternal education level. This variable represents socioeconomic and demographic characteristics that may influence infant growth.
  

## Inspect data
```{r}
str(dat)
summary(dat)
colSums(is.na(dat))

```

## Recode variables
```{r}
analysis_dat <- dat |>
  mutate(
    newid = factor(newid),

    # HIV exposure group:
    # Assuming "Positive" = infant exposed to maternal HIV (CHEU)
    # and "Negative" = HIV-unexposed (CHU)
    hiv_group = case_when(
      enrol_hiv_status_cat == "Positive" ~ "CHEU",
      enrol_hiv_status_cat == "Negative" ~ "CHU",
      TRUE ~ NA_character_
    ),
    hiv_group = factor(hiv_group, levels = c("CHU", "CHEU")),
    
     # Order visits chronologically
    visit = factor(visit, levels = c(
      "delivery",
      "week-3",
      "week-6",
      "month-3",
      "month-6",
      "month-9",
      "month-12",
      "month-18",
      "month-24"
    )),

    # Sex
    sex = factor(b1_sex),

    # Maternal age category
    momage_cat = factor(momage_cat),

    # Maternal education
    educ_cat_n = factor(educ_cat_n),

    # Breastfeeding variables
    ebf_updated = case_when(
      tolower(ebf_updated) %in% c("yes", "y") ~ "Yes",
      tolower(ebf_updated) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    ebf_updated = factor(ebf_updated, levels = c("No", "Yes")),

    bf_current_1year = case_when(
      tolower(bf_current_1year) %in% c("yes", "y") ~ "Yes",
      tolower(bf_current_1year) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    bf_current_1year = factor(bf_current_1year, levels = c("No", "Yes")),

    # Continuous variables
    infage_month = as.numeric(infage_month),
    gestage_final = as.numeric(gestage_final),
    zwfl = as.numeric(zwfl),
    zhc  = as.numeric(zhc)
  )
```

## Basic checks 
```{r}
# Number of infants and observations
analysis_dat |>
  summarise(
    n_obs = n(),
    n_infants = n_distinct(newid)
  )

# Outcome missingness
analysis_dat |>
  summarise(
    missing_zwfl = sum(is.na(zwfl)),
    missing_zhc  = sum(is.na(zhc))
  )

# Group counts
table(analysis_dat$hiv_group, useNA = "ifany")
table(analysis_dat$ebf_updated, useNA = "ifany")
table(analysis_dat$bf_current_1year, useNA = "ifany")

```
## Exploratory plots
```{r}
# Spaghetti plot for zwfl
p1 <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  ggplot(aes(x = infage_month, y = zwfl, group = newid, color = hiv_group)) +
  geom_line(alpha = 0.15) +
  geom_smooth(aes(group = hiv_group), method = "loess", se = TRUE, linewidth = 1.2) +
  labs(
    title = "Individual and average growth trajectories",
    x = "Infant age (months)",
    y = "Weight-for-length z-score (zwfl)",
    color = "Group"
  ) +
  theme_minimal()

# Mean profile by visit
p2 <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit, hiv_group) |>
  summarise(
    mean_zwfl = mean(zwfl, na.rm = TRUE),
    se_zwfl = sd(zwfl, na.rm = TRUE) / sqrt(sum(!is.na(zwfl))),
    .groups = "drop"
  ) |>
  ggplot(aes(x = visit, y = mean_zwfl, group = hiv_group, color = hiv_group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_zwfl - 1.96 * se_zwfl,
                    ymax = mean_zwfl + 1.96 * se_zwfl),
                width = 0.2) +
  labs(
    title = "Mean zwfl by visit",
    x = "Visit",
    y = "Mean zwfl",
    color = "Group"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p1 / p2
```
## Missingness 
```{r}
vis_miss(analysis_dat)
```

##  Main analysis dataset 
```{r}
# Keep observations needed for main model
main_dat <- analysis_dat |>
  filter(
    !is.na(zwfl),
    !is.na(hiv_group),
    !is.na(infage_month),
    !is.na(bf_current_1year),
    !is.na(ebf_updated),    
    !is.na(sex)
  )

```

# Model
```{r}
# Model 1
model1_zwfl <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 | newid),
  data = main_dat,
  REML = TRUE
)

# Model 2
model2_zwfl <- lmer(
  zwfl ~ hiv_group * bf_current_1year * infage_month +
         sex + (1 | newid),
  data = main_dat,
  REML = TRUE
)

summary(model1_zwfl)
anova(model1_zwfl)

summary(model2_zwfl)
anova(model2_zwfl)
```

```{r}
anova(model1_zwfl, model2_zwfl)
```
# Model diagnostics

```{r}
tidy(model1_zwfl, 
     effects = "fixed", 
     conf.int = TRUE) |>
  mutate(
    term = recode(term,
      "(Intercept)"                          = "Intercept",
      "hiv_groupCHEU"                        = "HIV group: CHEU vs CHU",
      "infage_month"                         = "Age (months)",
      "bf_current_1yearYes"                  = "Breastfeeding: Yes vs No",
      "sexmale"                              = "Sex: Male vs Female",
      "hiv_groupCHEU:infage_month"           = "CHEU × Age",
      "infage_month:bf_current_1yearYes"     = "Breastfeeding × Age",
      "hiv_groupCHEU:bf_current_1yearYes"    = "CHEU × Breastfeeding"
    ),
    across(c(estimate, conf.low, conf.high, std.error), ~round(.x, 3)),
    p.value = case_when(
      p.value < 0.001 ~ "<0.001",
      TRUE ~ as.character(round(p.value, 3))
    )
  ) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  rename(
    "Term" = term,
    "Estimate" = estimate,
    "SE" = std.error,
    "95% CI Lower" = conf.low,
    "95% CI Upper" = conf.high,
    "p-value" = p.value
  ) |>
  knitr::kable(align = "lrrrrr") 
```
