---
title: "CHL5222 Final Project"
subtitle: "Breastfeeding and HIV Exposure on Infant Growth"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)
```
# Libraries

```{r libraries}
library(tidyverse)
library(lme4)
library(lmerTest)
library(splines)
library(emmeans)
library(ggeffects)
library(broom.mixed)
library(patchwork)
library(janitor)
library(naniar)
library(knitr)
library(kableExtra)
library(ggplot2)
```


# Data Import

```{r import}
dat <- read.csv("hiv.csv", stringsAsFactors = FALSE) |>
  clean_names()
```

# Inspect Data

```{r}
str(dat)
summary(dat)
colSums(is.na(dat))
```

# Recode Variables

```{r}
analysis_dat <- dat |>
  mutate(
    newid = factor(newid),

    # HIV exposure group:
    # "Positive" maternal status = infant HIV-exposed uninfected (CHEU)
    # "Negative" maternal status = HIV-unexposed (CHU)
    hiv_group = case_when(
      enrol_hiv_status_cat == "Positive" ~ "CHEU",
      enrol_hiv_status_cat == "Negative" ~ "CHU",
      TRUE ~ NA_character_
    ),
    hiv_group = factor(hiv_group, levels = c("CHU", "CHEU")),

    # Order visits chronologically for plotting
    visit = factor(visit, levels = c(
      "delivery",
      "week-3",
      "week-6",
      "month-3",
      "month-6",
      "month-9",
      "month-12",
      "month-18",
      "month-24"
    )),

    # Infant sex
    sex = factor(b1_sex),

    # Maternal characteristics
    momage_cat = factor(momage_cat),
    educ_cat_n = factor(educ_cat_n),

    # Breastfeeding -- exclusive (ebf_updated)
    ebf_updated = case_when(
      tolower(ebf_updated) %in% c("yes", "y") ~ "Yes",
      tolower(ebf_updated) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    ebf_updated = factor(ebf_updated, levels = c("No", "Yes")),

    # Breastfeeding -- current at 1 year (bf_current_1year)
    bf_current_1year = case_when(
      tolower(bf_current_1year) %in% c("yes", "y") ~ "Yes",
      tolower(bf_current_1year) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    bf_current_1year = factor(bf_current_1year, levels = c("No", "Yes")),

    # Continuous variables
    infage_month  = as.numeric(infage_month),
    gestage_final = as.numeric(gestage_final),
    zwfl          = as.numeric(zwfl),

    # Mean-centred age: improves optimizer convergence and makes the intercept
    # interpretable as expected outcome at the mean observed age
    # Centred age: t* = t - mean(t)
    infage_month_c = infage_month - mean(infage_month, na.rm = TRUE)
  )
```


# Basic Checks

```{r}
# Number of infants and total observations
analysis_dat |>
  summarise(
    n_obs     = n(),
    n_infants = n_distinct(newid)
  )

# Outcome missingness
analysis_dat |>
  summarise(
    missing_zwfl = sum(is.na(zwfl))
  )

# Group counts
table(analysis_dat$hiv_group, useNA = "ifany")
table(analysis_dat$ebf_updated, useNA = "ifany")
table(analysis_dat$bf_current_1year, useNA = "ifany")
```


# Descriptive Statistics
```{r}
# Mean (SD) formatted string
fmt_mean_sd <- function(x) {
  x <- x[!is.na(x)]
  sprintf("%.1f (%.1f)", mean(x), sd(x))
}

# n (%) formatted string
fmt_n_pct <- function(x, level) {
  n_total <- sum(!is.na(x))
  n_level <- sum(x == level, na.rm = TRUE)
  sprintf("%d (%.1f%%)", n_level, 100 * n_level / n_total)
}

# Significance stars
pstar <- function(p) {
  dplyr::case_when(
    is.na(p)   ~ "",
    p < 0.001  ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ ""
  )
}

# Format p-value with stars
fmt_p <- function(p) {
  dplyr::case_when(
    is.na(p)   ~ "",
    p < 0.001  ~ paste0("<0.001", pstar(p)),
    TRUE ~ paste0(sprintf("%.3f", p), pstar(p))
  )
}
```

# Table 1: Infant and Maternal Characteristics at Baseline
```{r}
# One row per infant - baseline visit only
baseline_dat <- analysis_dat |>
  group_by(newid) |>
  slice_min(infage_month, with_ties = FALSE) |>
  ungroup()

chu  <- baseline_dat |> filter(hiv_group == "CHU")
cheu <- baseline_dat |> filter(hiv_group == "CHEU")
n_chu  <- nrow(chu)
n_cheu <- nrow(cheu)

tbl1 <- tribble(
  ~Characteristic, ~CHU, ~CHEU,
  # Infant sex
  "Infant sex, n (%)", "", "",
  "  Female",
    fmt_n_pct(chu$b1_sex,  "female"),
    fmt_n_pct(cheu$b1_sex, "female"),
  "  Male",
    fmt_n_pct(chu$b1_sex,  "male"),
    fmt_n_pct(cheu$b1_sex, "male"),
  # Gestational age
  "Gestational age (weeks), mean (SD)",
    fmt_mean_sd(chu$gestage_final),
    fmt_mean_sd(cheu$gestage_final),
  # Maternal age
  "Maternal age category, n (%)", "", "",
  "  25 years and under",
    fmt_n_pct(chu$momage_cat,  "25 and less"),
    fmt_n_pct(cheu$momage_cat, "25 and less"),
  "  26 to 35 years",
    fmt_n_pct(chu$momage_cat,  "26 to 35"),
    fmt_n_pct(cheu$momage_cat, "26 to 35"),
  "  Over 35 years",
    fmt_n_pct(chu$momage_cat,  "35 and more"),
    fmt_n_pct(cheu$momage_cat, "35 and more"),
  # Education
  "Maternal education, n (%)", "", "",
  "  Primary or below",
    fmt_n_pct(chu$educ_cat_n,  "Primary or below"),
    fmt_n_pct(cheu$educ_cat_n, "Primary or below"),
  "  Secondary and above",
    fmt_n_pct(chu$educ_cat_n,  "Secondary and above"),
    fmt_n_pct(cheu$educ_cat_n, "Secondary and above"),
  # Breastfeeding
  "Exclusively breastfed -- Yes, n (%)",
    fmt_n_pct(chu$ebf_updated[!is.na(chu$ebf_updated)],   "Yes"),
    fmt_n_pct(cheu$ebf_updated[!is.na(cheu$ebf_updated)], "Yes"),
  "Breastfeeding at 1 year -- Yes, n (%)",
    fmt_n_pct(chu$bf_current_1year[!is.na(chu$bf_current_1year)], "Yes"),
    fmt_n_pct(cheu$bf_current_1year[!is.na(cheu$bf_current_1year)], "Yes")
)

# Compute p-values for rows that need them
p_sex    <- chisq.test(table(baseline_dat$b1_sex, baseline_dat$hiv_group))$p.value
p_gest   <- t.test(gestage_final ~ hiv_group, data = baseline_dat)$p.value
p_momage <- chisq.test(table(baseline_dat$momage_cat, baseline_dat$hiv_group))$p.value
p_educ   <- chisq.test(table(baseline_dat$educ_cat_n, baseline_dat$hiv_group))$p.value
p_ebf    <- chisq.test(table(
  baseline_dat$ebf_updated[!is.na(baseline_dat$ebf_updated)],
  baseline_dat$hiv_group[ !is.na(baseline_dat$ebf_updated)]
))$p.value
p_bf1yr  <- chisq.test(table(
  baseline_dat$bf_current_1year[!is.na(baseline_dat$bf_current_1year)],
  baseline_dat$hiv_group[!is.na(baseline_dat$bf_current_1year)]
))$p.value

# Assign p-values to header rows; subrows left blank
tbl1$`p-value` <- c(
  fmt_p(p_sex),"", "", # sex header + 2 rows
  fmt_p(p_gest),                    # gestational age
  fmt_p(p_momage), "", "", "",      # maternal age header + 3 rows
  fmt_p(p_educ),   "", "",          # education header + 2 rows
  fmt_p(p_ebf),                     # exclusive BF
  fmt_p(p_bf1yr)                    # BF at 1 year
)

kable(
  tbl1,
  col.names = c(
    "Characteristic",
    paste0("CHU (n = ", n_chu, ")"),
    paste0("CHEU (n = ", n_cheu, ")"),
    "p-value"
  ),
  caption  = paste0(
    "Table 1. Baseline infant and maternal characteristics by HIV exposure group.",
    "Significance: *p<0.05, **p<0.01, ***p<0.001."
  ),
  booktabs = TRUE,
  align    = "lllr"
) |>
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    font_size     = 10
  ) |>
  row_spec(0, bold = TRUE) |>
  row_spec(c(1, 5, 9, 12), bold = TRUE) |>  
  footnote(
    general = paste0(
      "p-values: two-sample t-test for gestational age; ",
      "chi-squared test for all categorical variables."
    ),
    general_title     = "Note:",
    footnote_as_chunk = TRUE
  )
```

# Table 2: Summary of Growth Outcomes by HIV Group and Visit
```{r}
# Compute means and SDs per group per visit
growth_tbl <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit, hiv_group) |>
  summarise(
    n        = n(),
    m_zwfl   = mean(zwfl, na.rm = TRUE),
    sd_zwfl  = sd(zwfl,   na.rm = TRUE),
    .groups  = "drop"
  ) |>
  mutate(
    zwfl_fmt = sprintf("%.2f (%.2f)", m_zwfl, sd_zwfl)
  )

# t-test p-values per visit
pvals_visit <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit) |>
  summarise(
    p_zwfl = tryCatch(t.test(zwfl ~ hiv_group)$p.value, error = function(e) NA_real_),
    .groups = "drop"
  ) |>
  mutate(
    p_zwfl_fmt = fmt_p(p_zwfl)
  )

# Pivot wide: one row per visit
growth_wide <- growth_tbl |>
  select(visit, hiv_group, n, zwfl_fmt) |>
  pivot_wider(
    names_from  = hiv_group,
    values_from = c(n, zwfl_fmt)
  ) |>
  left_join(pvals_visit |> select(visit, p_zwfl_fmt),
            by = "visit") |>
  select(
    visit,
    n_CHU,  zwfl_fmt_CHU,
    n_CHEU, zwfl_fmt_CHEU,
    p_zwfl_fmt
  )

kable(
  growth_wide,
  col.names = c(
    "Visit",
    "N", "zwfl Mean (SD)",
    "N", "zwfl Mean (SD)",
    "p-value"
  ),
  caption  = paste0(
    "Table 2. Mean (SD) of weight-for-length Z-score (zwfl) by HIV exposure group and study visit. ",
    "Significance: *p<0.05, **p<0.01, ***p<0.001."
  ),
  booktabs = TRUE,
  align = "lrlrlc"
) |>
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    font_size = 9
  ) |>
  add_header_above(c(
    " " = 1,
    "CHU" = 2,
    "CHEU" = 2,
    "Group difference" = 1
  )) |>
  row_spec(0, bold = TRUE) |>
  footnote(
    general = paste0(
      "zwfl = weight-for-length Z-score. ",
      "p-values from two-sample t-test at each visit (unadjusted for multiple comparisons)."
    ),
    general_title = "Note:",
    footnote_as_chunk = TRUE
  )
```

# Figure 1: Individual Growth Trajectories and Mean Profiles (zwfl)

```{r}
theme_report1 <- function() {
  theme_classic(base_size = 11) +
    theme(
      plot.title       = element_blank(),
      legend.position  = "bottom",
      legend.title     = element_text(face = "bold", size = 10),
      legend.text      = element_text(size = 10),
      axis.title       = element_text(size = 11),
      axis.text        = element_text(size = 10),
      panel.grid.major = element_line(color = "grey90", linewidth = 0.3),
      panel.grid.minor = element_blank()
    )
}

hiv_colors <- c("CHU" = "#2166AC", "CHEU" = "#D6604D")

# Panel A: spaghetti + LOESS
fig1a <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  ggplot(aes(x = infage_month, y = zwfl,
             group = newid, color = hiv_group)) +
  geom_line(alpha = 0.12, linewidth = 0.3) +
  geom_smooth(aes(group = hiv_group),
              method = "loess", se = TRUE, linewidth = 1.2, span = 0.6) +
  scale_color_manual(values = hiv_colors,
                     labels = c("CHU"  = "HIV-unexposed (CHU)",
                                "CHEU" = "HIV-exposed uninfected (CHEU)")) +
  scale_x_continuous(
    breaks = c(1.5, 3, 6, 9, 12, 18, 24),
    labels = c("1.5", "3", "6", "9", "12", "18", "24")
  ) +
  labs(
    x     = "Infant age (months)",
    y     = "Weight-for-length Z-score",
    color = "HIV exposure group",
    tag   = "A"
  ) +
  theme_report() 

# Panel B: mean 95% CI at each visit
visit_levels <- c("delivery", "week-3", "week-6",
                  "month-3",  "month-6", "month-9",
                  "month-12", "month-18", "month-24")

fig1b <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  mutate(visit = factor(visit, levels = visit_levels)) |>
  group_by(visit, hiv_group) |>
  summarise(
    mean_zwfl = mean(zwfl, na.rm = TRUE),
    se_zwfl   = sd(zwfl, na.rm = TRUE) / sqrt(sum(!is.na(zwfl))),
    .groups   = "drop"
  ) |>
  ggplot(aes(x = visit, y = mean_zwfl,
             group = hiv_group, color = hiv_group)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2.2) +
  geom_errorbar(aes(ymin = mean_zwfl - 1.96 * se_zwfl,
                    ymax = mean_zwfl + 1.96 * se_zwfl),
                width = 0.25, linewidth = 0.6) +
  scale_color_manual(values = hiv_colors,
                     labels = c("CHU"  = "HIV-unexposed (CHU)",
                                "CHEU" = "HIV-exposed uninfected (CHEU)")) +
  labs(
    x     = "Study visit",
    y     = "Mean weight-for-length Z-score",
    color = "HIV exposure group",
    tag   = "B"
  ) +
  theme_report1() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

# Combine side by side with single shared legend
fig1_combined <- (fig1a | fig1b) +
  plot_layout(guides = "collect") &
  theme(
    legend.position  = "bottom",
    legend.direction = "horizontal"
  )

# Save 
ggsave("plots/fig1_combined.pdf", plot = fig1_combined,
       width = 13, height = 5.5, units = "in", device = cairo_pdf)
```

# Figure 2: Growth Trajectories Stratified by Breastfeeding Status
```{r}
theme_report2 <- function() {
  theme_classic(base_size = 11) +
    theme(
      plot.title       = element_blank(),
      legend.position  = "bottom",
      legend.title     = element_text(face = "bold", size = 9),
      legend.text      = element_text(size = 9),
      legend.key.width = unit(1.2, "cm"),      
      legend.spacing.y = unit(0.2, "cm"),
      legend.box       = "vertical",           
      axis.title       = element_text(size = 10),
      axis.text        = element_text(size = 9),
      panel.grid.major = element_line(color = "grey90", linewidth = 0.3),
      panel.grid.minor = element_blank()
    )
}

hiv_colors <- c("CHU" = "#2166AC", "CHEU" = "#D6604D")

visit_levels <- c("delivery", "week-3", "week-6",
                  "month-3",  "month-6", "month-9",
                  "month-12", "month-18", "month-24")

# Figure 2
fig2 <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group), !is.na(bf_current_1year)) |>
  mutate(visit = factor(visit, levels = visit_levels)) |>
  group_by(visit, hiv_group, bf_current_1year) |>
  summarise(
    mean_zwfl = mean(zwfl, na.rm = TRUE),
    se_zwfl   = sd(zwfl,  na.rm = TRUE) / sqrt(sum(!is.na(zwfl))),
    .groups   = "drop"
  ) |>
  ggplot(aes(
    x        = visit,
    y        = mean_zwfl,
    group    = interaction(hiv_group, bf_current_1year),
    colour   = hiv_group,
    linetype = bf_current_1year
  )) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.8) +
  geom_errorbar(
    aes(ymin = mean_zwfl - 1.96 * se_zwfl,
        ymax = mean_zwfl + 1.96 * se_zwfl),
    width = 0.2, linewidth = 0.5
  ) +
  scale_colour_manual(
    values = hiv_colors,
    labels = c("CHU"  = "HIV-unexposed (CHU)",
               "CHEU" = "HIV-exposed uninfected (CHEU)")
  ) +
  scale_linetype_manual(
    values = c("No" = "dashed", "Yes" = "solid"),
    labels = c("No"  = "Not breastfed at 1 year",
               "Yes" = "Breastfed at 1 year")
  ) +
  guides(
    colour   = guide_legend(order = 1, nrow = 1, title = "HIV exposure group"),
    linetype = guide_legend(order = 2, nrow = 1, title = "Breastfeeding status at 1 year")
  ) +
  labs(
    x        = "Study visit",
    y        = "Mean weight-for-length Z-score",
    colour   = "HIV exposure group",
    linetype = "Breastfeeding status at 1 year"
  ) +
  theme_report2() 

# Save
ggsave("plots/fig2_bf_hiv.pdf", plot = fig2,
       width = 6.5, height = 5.2, units = "in", device = cairo_pdf)
```

## Missingness

```{r missingness}
vis_miss(analysis_dat)
```

# Analytic Dataset

```{r}
# Complete cases for all primary model variables.
main_dat <- analysis_dat |>
  filter(
    !is.na(zwfl),
    !is.na(hiv_group),
    !is.na(infage_month),
    !is.na(bf_current_1year),
    !is.na(ebf_updated),
    !is.na(sex)
  )
```


# Statistical Model

```{r}
# first check if we need to add random slope
model1_zwfl <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 | newid),
  data = main_dat,
  REML = TRUE   
)

model1_zwfl_slope <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 + infage_month | newid),
  data = main_dat,
  REML = TRUE  
)

summary(model1_zwfl)
summary(model1_zwfl_slope)

# AIC comparison 
AIC(model1_zwfl, model1_zwfl_slope)
```

```{r}
# Model 1
model1_zwfl <- lmer(
  zwfl ~ sex + hiv_group + infage_month_c + bf_current_1year + 
    (1 + infage_month_c | newid),
  data = main_dat,
  REML = TRUE
)

# Model 2
model2_zwfl <- lmer(
  zwfl ~ hiv_group * infage_month_c + bf_current_1year +
    sex + (1 + infage_month_c | newid),
  data = main_dat,
  REML = TRUE
)


# Model 3
model3_zwfl <- lmer(
  zwfl ~ hiv_group * bf_current_1year * infage_month_c +
         sex + (1 + infage_month_c | newid),
  data = main_dat,
  REML = TRUE
)

summary(model1_zwfl)
summary(model2_zwfl)
summary(model3_zwfl)


anova(model1_zwfl, model2_zwfl)

anova(model2_zwfl, model3_zwfl)

```

## Final Model Parameter Estimates

```{r}
tidy(model1_zwfl,
     effects  = "fixed",
     conf.int = TRUE) |>
  mutate(
    term = dplyr::recode(term,
      "(Intercept)"                          = "Intercept",
      "hiv_groupCHEU"                        = "HIV group: CHEU vs CHU",
      "infage_month"                         = "Age (months)",
      "bf_current_1yearYes"                  = "Breastfeeding: Yes vs No",
      "sexmale"                              = "Sex: Male vs Female",
      "hiv_groupCHEU:infage_month"           = "CHEU x Age",
      "infage_month:bf_current_1yearYes"     = "Breastfeeding x Age",
      "hiv_groupCHEU:bf_current_1yearYes"    = "CHEU x Breastfeeding"
    ),
    across(c(estimate, std.error, conf.low, conf.high), ~round(.x, 3)),
    sig     = pstar(p.value),
    p.value = case_when(
      p.value < 0.001 ~ paste0("<0.001", sig),
      TRUE            ~ paste0(sprintf("%.3f", p.value), sig)
    )
  ) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  kable(
    col.names = c("Term", "Estimate", "SE",
                  "95% CI Lower", "95% CI Upper", "p-value"),
    caption   = paste0(
      "Table 3. Fixed effects estimates from final linear mixed effects model. ",
      "Primary outcome: weight-for-length Z-score (zwfl)."
    ),
    booktabs  = TRUE,
    align     = "lrrrrr"
  ) |>
  kable_styling(
    latex_options = "hold_position",
    font_size     = 12
  ) |>
  row_spec(0, bold = TRUE) |>
  footnote(
    general = paste0(
      "Estimates are change in zwfl per unit increase in the predictor. ",
      "Reference group: CHU, not breastfed, female, at mean age. "
    ),
    general_title     = "Note:",
    footnote_as_chunk = TRUE
  )
```
