---
title: "CHL5222 Final Project"
subtitle: "Breastfeeding and HIV Exposure on Infant Growth"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)
```

---

# Background

**Main outcome:** Weight-for-length z-score (`zwfl`)

HIV-exposed uninfected (CHEU) infants are children born to mothers living with HIV
who did not acquire the virus themselves, while HIV-unexposed (CHU) infants are born
to HIV-negative mothers. We compare growth trajectories between these groups and
assess whether breastfeeding modifies the relationship.

**Research objective:** To compare the growth trajectory of CHEU and CHU infants
over 0--24 months, and to assess whether breastfeeding modifies this relationship.

---

# Libraries

```{r libraries}
library(tidyverse)
library(lme4)
library(lmerTest)
library(splines)
library(emmeans)
library(ggeffects)
library(broom.mixed)
library(patchwork)
library(janitor)
library(naniar)
library(knitr)
library(kableExtra)
```

---

# Data Import

```{r import}
dat <- read.csv("hiv.csv", stringsAsFactors = FALSE) |>
  clean_names()
```

---

# Variable Descriptions

The dataset contains repeated growth measurements of infants followed from birth
to 24 months.

| Variable | Description |
|---|---|
| `newid` | Unique infant identifier |
| `visit` | Study visit |
| `infage_month` | Infant age (months) -- time dimension |
| `zwfl` | Weight-for-length Z-score (primary outcome) |
| `enrol_hiv_status_cat` | Maternal HIV status -- defines CHEU vs CHU |
| `ebf_updated` | Exclusive breastfeeding status |
| `bf_current_1year` | Breastfeeding status at 1 year |
| `b1_sex` | Infant sex |
| `gestage_final` | Gestational age at birth (weeks) |
| `momage_cat` | Maternal age category |
| `educ_cat_n` | Maternal education level |

---

# Inspect Data

```{r inspect}
str(dat)
summary(dat)
colSums(is.na(dat))
```

---

# Recode Variables

```{r recode}
analysis_dat <- dat |>
  mutate(
    newid = factor(newid),

    # HIV exposure group:
    # "Positive" maternal status = infant HIV-exposed uninfected (CHEU)
    # "Negative" maternal status = HIV-unexposed (CHU)
    hiv_group = case_when(
      enrol_hiv_status_cat == "Positive" ~ "CHEU",
      enrol_hiv_status_cat == "Negative" ~ "CHU",
      TRUE ~ NA_character_
    ),
    hiv_group = factor(hiv_group, levels = c("CHU", "CHEU")),

    # Order visits chronologically for plotting
    visit = factor(visit, levels = c(
      "delivery",
      "week-3",
      "week-6",
      "month-3",
      "month-6",
      "month-9",
      "month-12",
      "month-18",
      "month-24"
    )),

    # Infant sex
    sex = factor(b1_sex),

    # Maternal characteristics
    momage_cat = factor(momage_cat),
    educ_cat_n = factor(educ_cat_n),

    # Breastfeeding -- exclusive (ebf_updated)
    ebf_updated = case_when(
      tolower(ebf_updated) %in% c("yes", "y") ~ "Yes",
      tolower(ebf_updated) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    ebf_updated = factor(ebf_updated, levels = c("No", "Yes")),

    # Breastfeeding -- current at 1 year (bf_current_1year)
    bf_current_1year = case_when(
      tolower(bf_current_1year) %in% c("yes", "y") ~ "Yes",
      tolower(bf_current_1year) %in% c("no", "n")  ~ "No",
      TRUE ~ NA_character_
    ),
    bf_current_1year = factor(bf_current_1year, levels = c("No", "Yes")),

    # Continuous variables
    infage_month  = as.numeric(infage_month),
    gestage_final = as.numeric(gestage_final),
    zwfl          = as.numeric(zwfl),

    # Mean-centred age: improves optimizer convergence and makes the intercept
    # interpretable as expected outcome at the mean observed age (~13 months).
    # Centred age: t* = t - mean(t)
    infage_month_c = infage_month - mean(infage_month, na.rm = TRUE)
  )
```

---

# Basic Checks

```{r checks}
# Number of infants and total observations
analysis_dat |>
  summarise(
    n_obs     = n(),
    n_infants = n_distinct(newid)
  )

# Outcome missingness
analysis_dat |>
  summarise(
    missing_zwfl = sum(is.na(zwfl))
  )

# Group counts
table(analysis_dat$hiv_group,        useNA = "ifany")
table(analysis_dat$ebf_updated,      useNA = "ifany")
table(analysis_dat$bf_current_1year, useNA = "ifany")
```

---

# Descriptive Statistics
```{r desc-helpers, echo=FALSE}
# ── Helper functions for descriptive tables ──────────────────────────────────

# Mean (SD) formatted string
fmt_mean_sd <- function(x) {
  x <- x[!is.na(x)]
  sprintf("%.1f (%.1f)", mean(x), sd(x))
}

# n (%) formatted string
fmt_n_pct <- function(x, level) {
  n_total <- sum(!is.na(x))
  n_level <- sum(x == level, na.rm = TRUE)
  sprintf("%d (%.1f%%)", n_level, 100 * n_level / n_total)
}

# Significance stars
pstar <- function(p) {
  dplyr::case_when(
    is.na(p)   ~ "",
    p < 0.001  ~ "***",
    p < 0.01   ~ "**",
    p < 0.05   ~ "*",
    TRUE       ~ ""
  )
}

# Format p-value with stars
fmt_p <- function(p) {
  dplyr::case_when(
    is.na(p)   ~ "",
    p < 0.001  ~ paste0("<0.001", pstar(p)),
    TRUE       ~ paste0(sprintf("%.3f", p), pstar(p))
  )
}
```

## Table 1 -- Infant and Maternal Characteristics at Baseline

Baseline is defined as the earliest observation per infant (delivery visit).
Continuous variables: mean (SD); categorical: n (%).
Significance codes: \*p<0.05, \*\*p<0.01, \*\*\*p<0.001.

```{r table1}
# One row per infant -- baseline visit only
baseline_dat <- analysis_dat |>
  group_by(newid) |>
  slice_min(infage_month, with_ties = FALSE) |>
  ungroup()

chu  <- baseline_dat |> filter(hiv_group == "CHU")
cheu <- baseline_dat |> filter(hiv_group == "CHEU")
n_chu  <- nrow(chu)
n_cheu <- nrow(cheu)

# Build rows manually for full label control
tbl1 <- tribble(
  ~Characteristic,                         ~CHU,                                     ~CHEU,
  # --- Infant sex ---
  "Infant sex, n (%)",                       "",                                       "",
  "  Female",
    fmt_n_pct(chu$b1_sex,  "female"),
    fmt_n_pct(cheu$b1_sex, "female"),
  "  Male",
    fmt_n_pct(chu$b1_sex,  "male"),
    fmt_n_pct(cheu$b1_sex, "male"),
  # --- Gestational age ---
  "Gestational age (weeks), mean (SD)",
    fmt_mean_sd(chu$gestage_final),
    fmt_mean_sd(cheu$gestage_final),
  # --- Maternal age ---
  "Maternal age category, n (%)",            "",                                       "",
  "  25 years and under",
    fmt_n_pct(chu$momage_cat,  "25 and less"),
    fmt_n_pct(cheu$momage_cat, "25 and less"),
  "  26 to 35 years",
    fmt_n_pct(chu$momage_cat,  "26 to 35"),
    fmt_n_pct(cheu$momage_cat, "26 to 35"),
  "  Over 35 years",
    fmt_n_pct(chu$momage_cat,  "35 and more"),
    fmt_n_pct(cheu$momage_cat, "35 and more"),
  # --- Education ---
  "Maternal education, n (%)",               "",                                       "",
  "  Primary or below",
    fmt_n_pct(chu$educ_cat_n,  "Primary or below"),
    fmt_n_pct(cheu$educ_cat_n, "Primary or below"),
  "  Secondary and above",
    fmt_n_pct(chu$educ_cat_n,  "Secondary and above"),
    fmt_n_pct(cheu$educ_cat_n, "Secondary and above"),
  # --- Breastfeeding ---
  "Exclusively breastfed -- Yes, n (%)",
    fmt_n_pct(chu$ebf_updated[!is.na(chu$ebf_updated)],   "Yes"),
    fmt_n_pct(cheu$ebf_updated[!is.na(cheu$ebf_updated)], "Yes"),
  "Breastfeeding at 1 year -- Yes, n (%)",
    fmt_n_pct(chu$bf_current_1year[!is.na(chu$bf_current_1year)],   "Yes"),
    fmt_n_pct(cheu$bf_current_1year[!is.na(cheu$bf_current_1year)], "Yes")
)

# Compute p-values for rows that need them
p_sex    <- chisq.test(table(baseline_dat$b1_sex,        baseline_dat$hiv_group))$p.value
p_gest   <- t.test(gestage_final ~ hiv_group, data = baseline_dat)$p.value
p_momage <- chisq.test(table(baseline_dat$momage_cat,    baseline_dat$hiv_group))$p.value
p_educ   <- chisq.test(table(baseline_dat$educ_cat_n,    baseline_dat$hiv_group))$p.value
p_ebf    <- chisq.test(table(
  baseline_dat$ebf_updated[!is.na(baseline_dat$ebf_updated)],
  baseline_dat$hiv_group[ !is.na(baseline_dat$ebf_updated)]
))$p.value
p_bf1yr  <- chisq.test(table(
  baseline_dat$bf_current_1year[!is.na(baseline_dat$bf_current_1year)],
  baseline_dat$hiv_group[       !is.na(baseline_dat$bf_current_1year)]
))$p.value

# Assign p-values to header rows; subrows left blank
tbl1$`p-value` <- c(
  fmt_p(p_sex),    "", "",          # sex header + 2 rows
  fmt_p(p_gest),                    # gestational age
  fmt_p(p_momage), "", "", "",      # maternal age header + 3 rows
  fmt_p(p_educ),   "", "",          # education header + 2 rows
  fmt_p(p_ebf),                     # exclusive BF
  fmt_p(p_bf1yr)                    # BF at 1 year
)

kable(
  tbl1,
  col.names = c(
    "Characteristic",
    paste0("CHU (n = ", n_chu, ")"),
    paste0("CHEU (n = ", n_cheu, ")"),
    "p-value"
  ),
  caption  = paste0(
    "Table 1. Baseline infant and maternal characteristics by HIV exposure group.",
    "Significance: *p<0.05, **p<0.01, ***p<0.001."
  ),
  booktabs = TRUE,
  align    = "lllr"
) |>
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    font_size     = 10
  ) |>
  row_spec(0, bold = TRUE) |>
  row_spec(c(1, 5, 9, 12), bold = TRUE) |>   # bold category headers
  footnote(
    general = paste0(
      "p-values: two-sample t-test for gestational age; ",
      "chi-squared test for all categorical variables."
    ),
    general_title     = "Note:",
    footnote_as_chunk = TRUE
  )
```

---

## Table 2 -- Summary of Growth Outcomes by HIV Group and Visit

Mean (SD) of `zwfl` at each study visit by HIV exposure group.
Between-group differences tested with two-sample t-tests at each visit.
Significance codes: \*p<0.05, \*\*p<0.01, \*\*\*p<0.001.

```{r table2}
# Compute means and SDs per group per visit
growth_tbl <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit, hiv_group) |>
  summarise(
    n        = n(),
    m_zwfl   = mean(zwfl, na.rm = TRUE),
    sd_zwfl  = sd(zwfl,   na.rm = TRUE),
    .groups  = "drop"
  ) |>
  mutate(
    zwfl_fmt = sprintf("%.2f (%.2f)", m_zwfl, sd_zwfl)
  )

# t-test p-values per visit
pvals_visit <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit) |>
  summarise(
    p_zwfl = tryCatch(t.test(zwfl ~ hiv_group)$p.value, error = function(e) NA_real_),
    .groups = "drop"
  ) |>
  mutate(
    p_zwfl_fmt = fmt_p(p_zwfl)
  )

# Pivot wide: one row per visit
growth_wide <- growth_tbl |>
  select(visit, hiv_group, n, zwfl_fmt) |>
  pivot_wider(
    names_from  = hiv_group,
    values_from = c(n, zwfl_fmt)
  ) |>
  left_join(pvals_visit |> select(visit, p_zwfl_fmt),
            by = "visit") |>
  select(
    visit,
    n_CHU,  zwfl_fmt_CHU,
    n_CHEU, zwfl_fmt_CHEU,
    p_zwfl_fmt
  )

kable(
  growth_wide,
  col.names = c(
    "Visit",
    "N", "zwfl Mean (SD)",
    "N", "zwfl Mean (SD)",
    "p-value"
  ),
  caption  = paste0(
    "Table 2. Mean (SD) of weight-for-length Z-score (zwfl) by HIV exposure group and study visit. ",
    "Significance: *p<0.05, **p<0.01, ***p<0.001."
  ),
  booktabs = TRUE,
  align    = "lrlrlc"
) |>
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    font_size     = 9
  ) |>
  add_header_above(c(
    " "                = 1,
    "CHU"              = 2,
    "CHEU"             = 2,
    "Group difference" = 1
  )) |>
  row_spec(0, bold = TRUE) |>
  footnote(
    general = paste0(
      "zwfl = weight-for-length Z-score. ",
      "p-values from two-sample t-test at each visit (unadjusted for multiple comparisons)."
    ),
    general_title     = "Note:",
    footnote_as_chunk = TRUE
  )
```

---

# Exploratory Plots

## Figure 1 -- Individual Growth Trajectories and Mean Profiles (zwfl)

```{r fig1, fig.height=7, fig.width=7}
# Panel A: spaghetti plot with LOESS smoothed group means
p1 <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  ggplot(aes(x = infage_month, y = zwfl, group = newid, color = hiv_group)) +
  geom_line(alpha = 0.15) +
  geom_smooth(aes(group = hiv_group), method = "loess", se = TRUE, linewidth = 1.2) +
  labs(
    title = "Individual and average growth trajectories",
    x     = "Infant age (months)",
    y     = "Weight-for-length z-score (zwfl)",
    color = "Group"
  ) +
  theme_minimal()

# Panel B: mean +/- 95% CI at each visit
p2 <- analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group)) |>
  group_by(visit, hiv_group) |>
  summarise(
    mean_zwfl = mean(zwfl, na.rm = TRUE),
    se_zwfl   = sd(zwfl, na.rm = TRUE) / sqrt(sum(!is.na(zwfl))),
    .groups   = "drop"
  ) |>
  ggplot(aes(x = visit, y = mean_zwfl, group = hiv_group, color = hiv_group)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_zwfl - 1.96 * se_zwfl,
                    ymax = mean_zwfl + 1.96 * se_zwfl),
                width = 0.2) +
  labs(
    title = "Mean zwfl by visit",
    x     = "Visit",
    y     = "Mean zwfl",
    color = "Group"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p1 / p2
```

## Figure 2 -- Growth Trajectories Stratified by Breastfeeding Status

Mean zwfl +/- 95% CI at each visit, jointly stratified by HIV group and
breastfeeding status at 1 year. Motivates the interaction structure in
the statistical model.

```{r fig2, fig.height=5, fig.width=8}
analysis_dat |>
  filter(!is.na(zwfl), !is.na(hiv_group), !is.na(bf_current_1year)) |>
  group_by(visit, hiv_group, bf_current_1year) |>
  summarise(
    mean_zwfl = mean(zwfl, na.rm = TRUE),
    se_zwfl   = sd(zwfl, na.rm = TRUE) / sqrt(sum(!is.na(zwfl))),
    .groups   = "drop"
  ) |>
  ggplot(aes(
    x        = visit,
    y        = mean_zwfl,
    group    = interaction(hiv_group, bf_current_1year),
    colour   = hiv_group,
    linetype = bf_current_1year
  )) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 1.8) +
  geom_errorbar(
    aes(ymin = mean_zwfl - 1.96 * se_zwfl,
        ymax = mean_zwfl + 1.96 * se_zwfl),
    width = 0.2, linewidth = 0.5
  ) +
  scale_linetype_manual(
    values = c("No" = "dashed", "Yes" = "solid"),
    labels = c("No" = "Not breastfed at 1 year",
               "Yes" = "Breastfed at 1 year")
  ) +
  labs(
    title    = "Mean zwfl by HIV group and breastfeeding status",
    x        = "Visit",
    y        = "Mean zwfl",
    colour   = "HIV Group",
    linetype = "Breastfeeding at 1 year"
  ) +
  theme_minimal() +
  theme(
    axis.text.x     = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )
```

## Missingness

```{r missingness}
vis_miss(analysis_dat)
```

---

# Analytic Dataset

```{r main-dataset}
# Complete cases for all primary model variables.
# Excludes: 37 missing zwfl, 22 missing bf_current_1year, 5 missing ebf_updated.
main_dat <- analysis_dat |>
  filter(
    !is.na(zwfl),
    !is.na(hiv_group),
    !is.na(infage_month),
    !is.na(bf_current_1year),
    !is.na(ebf_updated),
    !is.na(sex)
  )
```

---

# Statistical Model

## Model Specification

We fit a **linear mixed effects model** (LME) to account for the correlation
of repeated measures within each infant. The general model is:

$$Y_{ij} = \beta_0 + \beta_1 H_i + \beta_2 B_i + \beta_3 t^*_{ij} + \beta_4 S_i
           + \text{interactions} + u_i + \varepsilon_{ij}$$

where:

- $Y_{ij}$ = zwfl for infant $i$ at time $j$  
- $H_i$ = HIV group (0 = CHU, 1 = CHEU)  
- $B_i$ = breastfeeding status (0 = No, 1 = Yes)  
- $t^*_{ij}$ = mean-centred age in months: $t^* = t - \bar{t}$  
- $S_i$ = infant sex (0 = Female, 1 = Male)  
- $u_i \sim \mathcal{N}(0, \sigma^2_u)$ = random intercept per infant  
- $\varepsilon_{ij} \sim \mathcal{N}(0, \sigma^2)$ = residual error  

Mean-centring age improves optimizer convergence and makes $\beta_0$
interpretable as expected zwfl at the **mean observed age** rather than at birth.

## Stage 1 -- Random Effects Structure Selection (REML = TRUE)

We use **AIC** with `REML = TRUE` (required for comparing random effects
structures) to choose between:

$$\text{Random intercept only: } \quad u_i \sim \mathcal{N}(0,\, \sigma^2_u)$$

$$\text{Random intercept + slope: } \quad \begin{pmatrix} u_i \\ v_i \end{pmatrix} \sim \mathcal{N}\!\left(\mathbf{0},\, \boldsymbol{\Sigma}\right), \quad \boldsymbol{\Sigma} = \begin{pmatrix} \sigma^2_u & \rho\sigma_u\sigma_v \\ \rho\sigma_u\sigma_v & \sigma^2_v \end{pmatrix}$$

```{r random-effects-selection}
# first check if we need to add random slope
model1_zwfl <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 | newid),
  data = main_dat,
  REML = TRUE   # REML = TRUE required for random effects comparison
)

model1_zwfl_slope <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 + infage_month | newid),
  data = main_dat,
  REML = TRUE   # REML = TRUE required for random effects comparison
)

summary(model1_zwfl)
summary(model1_zwfl_slope)

# AIC comparison -- lower AIC = preferred random effects structure
AIC(model1_zwfl, model1_zwfl_slope)
```

## Stage 2 -- Fixed Effects Model Comparison (REML = FALSE)

Using the random effects structure selected above, we compare two
pre-specified models with **REML = FALSE** for valid likelihood ratio testing.

**Model 1** (two-way interactions):
$$Y_{ij} = \beta_0 + \beta_1 H_i + \beta_2 B_i + \beta_3 t^*_{ij} + \beta_4 S_i
           + \beta_5(H_i \cdot t^*_{ij})
           + \beta_6(B_i \cdot t^*_{ij})
           + \beta_7(H_i \cdot B_i)
           + u_i + \varepsilon_{ij}$$

**Model 2** (three-way interaction -- research question):
$$Y_{ij} = \beta_0 + \cdots + \beta_7(H_i \cdot B_i)
           + \underbrace{\beta_8(H_i \cdot B_i \cdot t^*_{ij})}_{\text{key term: }H_0:\,\beta_8 = 0}
           + u_i + \varepsilon_{ij}$$

$\beta_8$ tests whether breastfeeding **differentially** modifies the CHEU vs CHU
growth trajectory over time -- the direct answer to the research objective.

```{r models}
# Update random structure below based on Stage 1 AIC result:
#   Random intercept only  --> (1 | newid)
#   Random slope included  --> (1 + infage_month | newid)

# Model 1: all two-way interactions (REML = FALSE for fixed effects comparison)
model1_zwfl <- lmer(
  zwfl ~ hiv_group * infage_month +
         bf_current_1year * infage_month + 
         hiv_group * bf_current_1year + 
         sex + (1 + infage_month | newid),
  data = main_dat,
  REML = FALSE
)

# Model 2: three-way interaction -- directly tests the research question
# H0: beta_8 = 0 (breastfeeding does NOT differentially modify HIV-growth trajectory)
# H1: beta_8 != 0 (breastfeeding DOES modify the HIV-growth trajectory)
model2_zwfl <- lmer(
  zwfl ~ hiv_group * bf_current_1year * infage_month +
         sex + (1 + infage_month | newid),
  data = main_dat,
  REML = FALSE
)

summary(model1_zwfl)
anova(model1_zwfl)

summary(model2_zwfl)
anova(model2_zwfl)
```

```{r model-comparison}
# Likelihood ratio test: Model 1 vs Model 2
# 1 degree of freedom (adds only beta_8)
# p < 0.05 --> report Model 2 (BF modifies HIV-growth trajectory)
# p >= 0.05 --> report Model 1 (no differential modification by BF)
anova(model1_zwfl, model2_zwfl)
```

## Final Model Parameter Estimates

```{r results-table}
# Refit chosen (final) model with REML = TRUE for unbiased parameter estimates
# Update model formula below based on model comparison result above

tidy(model1_zwfl,
     effects  = "fixed",
     conf.int = TRUE) |>
  mutate(
    term = dplyr::recode(term,
      "(Intercept)"                          = "Intercept",
      "hiv_groupCHEU"                        = "HIV group: CHEU vs CHU",
      "infage_month"                         = "Age (months)",
      "bf_current_1yearYes"                  = "Breastfeeding: Yes vs No",
      "sexmale"                              = "Sex: Male vs Female",
      "hiv_groupCHEU:infage_month"           = "CHEU x Age",
      "infage_month:bf_current_1yearYes"     = "Breastfeeding x Age",
      "hiv_groupCHEU:bf_current_1yearYes"    = "CHEU x Breastfeeding"
    ),
    across(c(estimate, std.error, conf.low, conf.high), ~round(.x, 3)),
    sig     = pstar(p.value),
    p.value = case_when(
      p.value < 0.001 ~ paste0("<0.001", sig),
      TRUE            ~ paste0(sprintf("%.3f", p.value), sig)
    )
  ) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  kable(
    col.names = c("Term", "Estimate", "SE",
                  "95% CI Lower", "95% CI Upper", "p-value"),
    caption   = paste0(
      "Table 3. Fixed effects estimates from final linear mixed effects model. ",
      "Primary outcome: weight-for-length Z-score (zwfl). ",
      "Significance: *p<0.05, **p<0.01, ***p<0.001."
    ),
    booktabs  = TRUE,
    align     = "lrrrrr"
  ) |>
  kable_styling(
    latex_options = "hold_position",
    font_size     = 12
  ) |>
  row_spec(0, bold = TRUE) |>
  footnote(
    general = paste0(
      "Estimates are change in zwfl per unit increase in the predictor. ",
      "Reference group: CHU, not breastfed, female, at mean age. ",
      "Model fitted with REML = TRUE."
    ),
    general_title     = "Note:",
    footnote_as_chunk = TRUE
  )
```
